\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle[shortrules]{banking}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}
\usepackage{combelow}

% create new hlink command; this is needed, since \httplink only supports http:// links.
% also overwrite \httplink to point to HTTPS addresses.
\makeatletter
\newcommand*{\hlink}[2][]{%
	\ifthenelse{\equal{#1}{}}%
	{\href{#2}{#2}}%
	{\href{#2}{#1}}}
\renewcommand*{\httplink}[2][]{%
	\ifthenelse{\equal{#1}{}}%
	{\href{https://#2}{#2}}%
	{\href{https://#2}{#1}}}
\makeatother

% redefine social region to support skype.
\makeatletter
\newcommand*{\skypesocialsymbol}{\faSkype~}
\RenewDocumentCommand{\social}{O{}O{}m}{%
	\ifthenelse{\equal{#2}{}}%
    {%
    	\ifthenelse{\equal{#1}{linkedin}}{\collectionadd[linkedin]{socials}{\protect\httplink[#3]{www.linkedin.com/in/#3}}}{}%
    	\ifthenelse{\equal{#1}{twitter}} {\collectionadd[twitter]{socials} {\protect\httplink[#3]{www.twitter.com/#3}}}    {}%
    	\ifthenelse{\equal{#1}{facebook}}{\collectionadd[facebook]{socials}{\protect\httplink[#3]{www.facebook.com/#3}}}   {}%
    	\ifthenelse{\equal{#1}{github}}  {\collectionadd[github]{socials}  {\protect\httplink[#3]{github.com/#3}}}     {}%
    	\ifthenelse{\equal{#1}{skype}}   {\collectionadd[skype]{socials}   {\protect\hlink[#3]{skype:#3}}}              {}%
    }
    {\collectionadd[#1]{socials}{\protect\httplink[#3]{#2}}}}
\makeatother

\name{Roland}{Bogosi}
\title{Résumé}
\email{root@rolisoft.net}
\homepage{rolisoft.net}
\social[linkedin]{RolandBogosi}
\social[skype]{RoliSoft}
\social[github]{RoliSoft}
\quote{"Knowing is not enough; we must apply. Willing is not enough; we must do." - Johann Wolfgang von Goethe}

\input{info_intl.tex}

\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
\begin{document}
\makecvtitle

\section{Education}

	\cventry{September 2012--July 2016}{B.Sc. Computer Engineering}{Sapientia EMTE, Faculty of Technical and Human Sciences}{Târgu-Mure\cb{s}}{}{Gave multiple presentations in various fields; attended the XVI. Scientific Student Conference with a project which won a special award; participated in a research group studying sentiment analysis as an extracurricular activity; doing thesis in the field of Information Security.}

\section{Experience}
	
	\cventry{December 2013--December 2015}{DevOps Engineer and Full-Stack Developer}{BrightAlien Ltd}{London (Remote)}{}{Job responsibilities include the full-stack development of 9 websites plus an internal dashboard; the installation with continued proactive monitoring and administration of 4 *nix-based and 1 Windows-based production servers; miscellaneous DevOps responsibilities.}

	\cventry{July 2014--August 2014}{Android Developer Internship}{Lynx Solutions SRL}{Târgu-Mure\cb{s}}{}{Job responsibilities included the creation of a 30-page document describing the application to be developed and its specifications; the single-handed development of the documented Android-based application with UI accommodating both smartphones and tablets alike (through the use of fragments and multiple layouts with constraints); overseeing fellow interns through their journey of implementing the documented REST API.}

\section{Certifications}

	\cvitemwithcomment{}{\textbf{IPv6 Certified Sage}, Hurricane Electric}{March 2011}

\section{Publications}

	\cvitem{Sapiness Sentiment Analyser}{Katalin Tünde Jánosi-Rancz, Zoltán Kátai and Roland Bogosi; \textit{Acta Universitatis Sapientiae, Informatica,} vol. 7, no. 2, pp. 186--199, 2015.}

\section{Languages}

	\cvitem{English}{Full professional proficiency}
	\cvitem{Hungarian, Romanian}{Native or bilingual proficiency}

\section{Technical Skills}
	\subsection{Proficient with}
	
		\cvline{Languages}{C/C++ \textit{(8 years)}, C\# \textit{(10 years)}, Java \textit{(9 years)}, Go, Python, PHP \textit{(12 years)}, JavaScript, SQL}
		\cvline{Libraries}{STL, Boost, Qt, MFC, Swing, WinForms, WPF, C++/CLI, NUnit, jQuery, Bootstrap, Angular.js, PHPUnit...}
		\cvline{Technologies}{Android, Android NDK, Debian, CentOS, BSD, nginx, Apache, HHVM, exim, Postfix, Redis, memcached, ElasticSearch, Sphinx, MySQL/MariaDB, SQLite, Oracle, SOAP, JSON, Google ProtoBuf, XDebug, OpenVPN, L2TP/IPSec, Radius/LDAP, Tor/I2P, Meshnets, Google AppEngine, Amazon AWS/Linode/DigitalOcean, CloudFlare/Incapsula, NSIS, InnoSetup, WiX, MSTest, dotCover, dotMemory, dotTrace...}
		\cvline{Fields}{Penetration testing, Reverse engineering, System administration, Shell programming, Task automation, High availability (Load-balancing, TTFB optimization...), Software performance, Server/software security, Data encryption, Networking, Screen scraping, Testing, Search engine optimization (SEO), Continuous Integration}
		
	\subsection{Exposure to}
	
		\cvline{Languages}{Matlab, VHDL, CAPL, Ruby, PowerShell}
		\cvline{Technologies}{OpenCL, Cuda, PostgreSQL, Microsoft SQL Server, MongoDB, CouchDB}
		\cvline{Fields}{Massively parallel systems, Neural networks, Recommendations systems}

\section{Interests}
	\textbf{Self-teaching} is an important part of my lifestyle. I try to keep up with the ever-evolving technologies of today. I constantly \textbf{try out new languages}, \textbf{new technologies} and \textbf{new practices}. I constantly go back and \textbf{re-do old projects}, with a twist, and I challenge myself to do it much better this time, by setting much higher goals. I read \textbf{research papers}, \textbf{0-day bulletins} and other sources of information that let me be ahead of the competition. I am not afraid to take initiative, and to color outside of the lines. I don't mind to get my hands dirty to try something out, let it be DoS-ing my own server in order to try out if an optimization technique or security practice did indeed work. I also watch \textbf{conference videos} (such as \textbf{DefCon}, \textbf{Black Hat}, etc) and \textbf{tech-talks} (such as \textbf{Microsoft's GoingNative}, and much more) in order to get an edge in their specific fields.
	\\\\
	{\color{color2} A more detailed description of my technical skills, list of personal projects and extracurricular activities is available in my Curriculum Vit\ae, which can be downloaded from}
	{\color{color1} \url{https://rolisoft.net/cv.pdf}}
	
\end{document}